---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Containment and connectivity in Dutch urban systems: A network-analytical operationalization of the three-systems model."
```

# tesgcontainmentconnectivity

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/atepoorthuis/containment-connectivity-urban-systems/master?urlpath=rstudio)

This repository contains the data and code for our paper:

> Poorthuis, A and M. van Meeteren, (2019). _`r Title`_. Tijdschrift voor Economische en Sociale Geografie <https://doi.org/10.1111/tesg.12391>

Our pre-print is online here:

> Poorthuis, A and M. van Meeteren, (2019). _`r Title`_. Tijdschrift voor Economische en Sociale Geografie, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

This repository contains all the data and code needed to reproduce the results and figures in our paper.

- [analysis/01-prepare-network-data.Rmd](analysis/01-prepare-network-data.md): Prepare network data and perform community detection
- [analysis/02-analysis-figures.Rmd](analysis/02-analysis-figures.md): Process the community detection results for the different urban systems and create the figures included in the paper.

All necessary data can be found in `analysis/data/raw_data/`.

### How to download or install

You can download the compendium as a zip from from [this URL](https://github.com/atepoorthuis/containment-connectivity-urban-systems/archive/master.zip)

Or you can install this compendium as an R package, tesgcontainmentconnectivity, from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
remotes::install_github("atepoorthuis/containment-connectivity-urban-systems")
```


### Licenses

Text + figures and data:  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

Code: See the [DESCRIPTION](DESCRIPTION) file
