---
title: "Analysis & Figures"
author: "Ate Poorthuis"
date: "11/10/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(here)
library(sf)
library(rmapshaper)
library(patchwork)
library(tmap)
library(purrr)
```

## Load results of community detection
We first load the results of the community detection procedure from the `.tree` files generated by Infomap for each of the three systems.

```{r}
# we need the postcode data again so load that first
postcode <- st_read(here("analysis", "data", "raw_data", "postcode_polygons", "CBS_ESRI_PC4_2017.shp"), crs = 28992, stringsAsFactors = F) %>% 
  mutate(pc4 = as.integer(pc4)) %>% 
  ms_simplify(keep_shapes = T) %>%  # pc geometry is much more detailed than we need, simplify
  st_buffer(dist = 0)

isolates <- read_rds(here("analysis", "data", "derived_data", "isolate_postcodes.rds"))
```

```{r message=F}
dus <-
  read_csv(here("analysis", "data", "raw_data", "dus_pc_edges.csv"))
dus_com <- map(seq(0.10, 6, by = 0.10), function(i) {
  tesgcontainmentconnectivity::com_extract(here(
    "analysis",
    "data",
    "derived_data",
    "dus-communities",
    paste0("dus-", i, ".tree")
  ))
})
dus_stats <- tibble(
  markov = seq(0.10, 6, by = 0.10),
  members = map_int(dus_com, tesgcontainmentconnectivity::com_count),
  codeLength = map_chr(seq(0.10, 6, by = 0.10), function(i) {
    tesgcontainmentconnectivity::codeLength_extract(here(
      "analysis",
      "data",
      "derived_data",
      "dus-communities",
      paste0("dus-", i, ".tree")
    ))
  }),
  external = map_dbl(dus_com, function(com)
    tesgcontainmentconnectivity::com_external(com, totalFlow = dus, isolates = isolates)),
  externalMedian = map_dbl(dus_com, function(com)
    tesgcontainmentconnectivity::com_externalMedian(com, totalFlow = dus, isolates = isolates))
) %>%
  mutate(codeLength = as.numeric(codeLength))
dus_stats    
```

```{r message=F}
centralplace <-
  read_csv(here("analysis", "data", "raw_data", "centralplace_pc_edges.csv"))
cp_com <- map(seq(0.10, 7, by = 0.10), function(i) {
  tesgcontainmentconnectivity::com_extract(here(
    "analysis",
    "data",
    "derived_data",
    "cp-communities",
    paste0("cp-", i, ".tree")
  ))
})

cp_stats <- tibble(
  markov = seq(0.10, 7, by = 0.10),
  members = map_int(cp_com, tesgcontainmentconnectivity::com_count),
  codeLength = map_chr(seq(0.10, 7, by = 0.10), function(i) {
    tesgcontainmentconnectivity::codeLength_extract(here(
      "analysis",
      "data",
      "derived_data",
      "cp-communities",
      paste0("cp-", i, ".tree")
    ))
  }),
  external = map_dbl(cp_com, function(com)
    tesgcontainmentconnectivity::com_external(com, totalFlow = centralplace, isolates = isolates)),
  externalMedian = map_dbl(cp_com, function(com)
    tesgcontainmentconnectivity::com_externalMedian(com, totalFlow = centralplace, isolates = isolates))
) %>%
  mutate(codeLength = as.numeric(codeLength))
cp_stats                  
```

```{r message=F}
export <-
  read_csv(here("analysis", "data", "raw_data", "export_pc_edges.csv"))
ex_com <- map(seq(0.15, 7, by = 0.15), function(i) {
  tesgcontainmentconnectivity::com_extract(here(
    "analysis",
    "data",
    "derived_data",
    "ex-communities",
    paste0("ex-", i, ".tree")
  ))
})
ex_stats <- tibble(
  markov = seq(0.15, 7, by = 0.15),
  members = map_int(ex_com, tesgcontainmentconnectivity::com_count),
  codeLength = map_chr(seq(0.15, 7, by = 0.15), function(i) {
    tesgcontainmentconnectivity::codeLength_extract(here(
      "analysis",
      "data",
      "derived_data",
      "ex-communities",
      paste0("ex-", i, ".tree")
    ))
  }),
  external = map_dbl(ex_com, function(com)
    tesgcontainmentconnectivity::com_external(com, totalFlow = export, isolates = isolates)),
  externalMedian = map_dbl(ex_com, function(com)
    tesgcontainmentconnectivity::com_externalMedian(com, totalFlow = export, isolates = isolates))
)
ex_stats                  
```

```{r}
# set 'chosen' urban system based on theoretical cut-off
dus_i <- which.min(dus_stats$external > 0.05)
cp_i <- which.min(cp_stats$external > 0.01)
ex_i <- which.min(ex_stats$external > 0.06)
```

## Merge isolates postcodes with their nearest neighbor
We calculate a distance matrix between all postcodes and merge isolates with their nearest neighbor based on this matrix. This is so the resulting maps are not 'cluttered' with isolated postcodes.
```{r cache = TRUE}
filter_out <- postcode %>% 
  left_join(ex_com[[ex_i]], by=c("pc4" = "name")) %>% 
  rename("exp" = "community") %>% 
  left_join(cp_com[[cp_i]], by=c("pc4" = "name")) %>% 
  rename("cp" = "community") %>% 
  left_join(dus_com[[dus_i]], by=c("pc4" = "name")) %>% 
  rename("dus" = "community") %>% 
  as_tibble() %>%
  filter((is.na(exp) | is.na(cp) | is.na(dus))) %>% 
  st_as_sf()

filter_in <- postcode %>% 
  left_join(ex_com[[ex_i]], by=c("pc4" = "name")) %>% 
  rename("exp" = "community") %>% 
  left_join(cp_com[[cp_i]], by=c("pc4" = "name")) %>% 
  rename("cp" = "community") %>% 
  left_join(dus_com[[dus_i]], by=c("pc4" = "name")) %>% 
  rename("dus" = "community") %>% 
  as_tibble() %>%
  filter(!(is.na(exp) | is.na(cp) | is.na(dus))) %>% 
  st_as_sf()

dist <- st_distance(filter_in, filter_out)
filter_replace <- filter_out %>% 
  mutate(index = row_number()) %>% 
  rowwise() %>% 
  mutate(closest = which.min(dist[,index])) %>% 
  rowwise() %>% 
  mutate(merge_with = filter_in[closest,]$pc4) %>% 
  select(pc4, merge_with)

postcode_with_isolates_merged <- postcode %>%
  left_join(filter_replace, by = c("pc4" = "pc4")) %>% 
  mutate(merge_with=coalesce(merge_with,pc4)) %>% 
  mutate(pc4 = merge_with) %>% 
  select(pc4) %>% 
  group_by(pc4) %>% 
  summarise(count = n()) %>% 
  ms_simplify(keep = 0.9, keep_shapes = T) %>% 
  st_buffer(dist = 0)
```

## Figure 2
```{r fig.height = 6}
p1 <- dus_stats %>% 
  ggplot() + geom_line(aes(x = markov, y = members)) + xlab("Markov Time") + ylab("Number of Regions")

p2 <- dus_stats %>% 
  ggplot() + geom_line(aes(x = markov, y = external)) + xlab("Markov Time") + ylab("% of interactions to/from outside region") +
  annotate("text", x = 3.1, y = 0.05, hjust = 0, vjust = 0.4, label = "nodalization cut-off point", fontface = "italic") + 
  annotate("segment", x = 1.6, xend = 3, y = 0.05, yend = 0.05, color = "darkgray") +
  annotate("point", x = dus_stats$markov[5], y = dus_stats$external[5]) +
  annotate("point", x = dus_stats$markov[9], y = dus_stats$external[9]) +
  annotate("point", x = dus_stats$markov[13], y = dus_stats$external[13]) +
  annotate("point", x = dus_stats$markov[25], y = dus_stats$external[25])

p1 + p2 + plot_layout(ncol = 1)
# ggsave("Figure 2a.pdf", height = 6)

map1 <- tesgcontainmentconnectivity::comm_merge(dus_com[[5]], postcode_with_isolates_merged, dus_i) %>% 
  ms_simplify(keep = 0.9, keep_shapes = T) %>%  # clean up some weird lines after merging
  tm_shape() + tm_borders(lwd = 0.5, col = "black") + tm_layout(frame = F) + tm_layout(title = "Markov Time 0.5", title.size = 0.9)

map2 <- tesgcontainmentconnectivity::comm_merge(dus_com[[9]], postcode_with_isolates_merged, dus_i) %>% 
  ms_simplify(keep = 0.9, keep_shapes = T) %>%  # clean up some weird lines after merging
  tm_shape() + tm_borders(lwd = 0.5, col = "black") + tm_layout(frame = F) + tm_layout(title = "Markov Time 0.9", title.size = 0.9)

map3 <- tesgcontainmentconnectivity::comm_merge(dus_com[[13]], postcode_with_isolates_merged, dus_i) %>% 
  ms_simplify(keep = 0.9, keep_shapes = T) %>%  # clean up some weird lines after merging
  tm_shape() + tm_borders(lwd = 0.5, col = "black") + tm_layout(frame = F) + tm_layout(title = "Markov Time 1.3", title.size = 0.9)

map4 <- tesgcontainmentconnectivity::comm_merge(dus_com[[25]], postcode_with_isolates_merged, dus_i) %>% 
  ms_simplify(keep = 0.9, keep_shapes = T) %>%  # clean up some weird lines after merging
  tm_shape() + tm_borders(lwd = 0.5, col = "black") + tm_layout(frame = F) + tm_layout(title = "Markov Time 2.5", title.size = 0.9)

tmap_arrange(list(map1, map2, map3, map4), ncol = 2)
# tmap_save(tmap_arrange(list(map1, map2, map3, map4), ncol = 2), filename = "Figure2b.pdf", height = 6)
```

## Figure 3
We need a background layer to indicate towns/built-up areas. We use the TOP10NL built-up place layer ('plaats'). Easy-to-use extracts used to be provided [by Jan-Willem van Aalst at Imergis](https://www.imergis.nl/htm/opendata.htm) but as of 1 November 2019, they are no longer available. Instead, download TOP10NL data directly from [PDOK](https://www.pdok.nl/introductie/-/article/basisregistratie-topografie-brt-topnl). TOP10NL data is made available by the Dutch Kadaster as part of the Basisregistratie Topografie (BRT) under a CC BY 4.0 license.

```{r}
towns <- st_read(here("analysis", "data", "raw_data", "top10_buildup", "Top10NL-Plaats_kern.shp")) %>% 
  select(naamnl) %>% 
  ms_simplify(keep = 0.09) %>% 
  st_buffer(dist = 0)
towns_plot <- tm_shape(towns) + tm_fill(col = "#2F4F4F", alpha = 0.5)
```


```{r fig.height = 4.5, fig.width = 7.5}
# the edges between communities in the DUS are based on commuting flows
dus_flow <- read_csv(here("analysis", "data", "raw_data", "export_pc_edges.csv"))
dus_flow <- tesgcontainmentconnectivity::merge_flow(dus_flow, dus_com[[dus_i]], isolates)

dus_final <- tesgcontainmentconnectivity::com_statsPerCom(dus_com[[dus_i]], dus, isolates) %>% 
  filter(internal > 1000)
dus_final_sf <- tesgcontainmentconnectivity::comm_merge(dus_com[[dus_i]], postcode_with_isolates_merged, dus_i) %>% 
  left_join(dus_final, by = c("community" = "com")) %>% 
  ms_simplify(keep = 0.9, keep_shapes = T) # clean up some weird lines after merging

dus_centroid <- st_centroid(tesgcontainmentconnectivity::comm_merge(dus_com[[dus_i]], postcode_with_isolates_merged, dus_i)) %>%
  select(community) %>%
  left_join(., dus_final, by = c("community" = "com"))

dus_lines <- dus_flow %>%
  left_join(dus_centroid, by = c("source" = "community")) %>%
  left_join(dus_centroid, by = c("sink" = "community")) %>%
  drop_na() %>% 
  filter(weight > 100) %>% # filter very small interactions
  rowwise() %>%
  mutate(geometry = st_combine(c(geometry.x, geometry.y)) %>% st_cast("LINESTRING")) %>% select(-geometry.x, -geometry.y) %>%
  st_as_sf(crs = 28992)

dus_outline <- tm_shape(dus_final_sf) + tm_borders(lwd = 0.9, col = "#383838")

dus_fill <-
  tm_shape(dus_final_sf) + tm_fill(
    col = "outgoingRel",
    style = "jenks",
    palette = "YlGn",
    showNA = F,
    legend.is.portrait = F,
    title = "% Outgoing Interaction"
  ) +
  tm_legend(
    legend.position = c("left", "bottom"),
    legend.width = 0.55,
    legend.format = list(
      text.separator = "to",
      fun = function(x)
        paste0(formatC(
          x * 100, digits = 1, format = "f"
        ), "%")
    )
  )

dus_fill_no_legend <- tm_shape(dus_final_sf) +
  tm_fill(
    col = "outgoingRel",
    palette = "YlGn",
    showNA = F,
    n = 5,
    style = "jenks",
    legend.is.portrait = F,
    title = "Incoming Interactions",
    legend.show = F
  ) +
  tm_legend(legend.position = c("left", "bottom"),
            legend.width = 0.55)

dus_line_plot <-
  tm_shape(dus_lines) + tm_lines(
    col = "#B02430",
    lwd = "weight",
    alpha = 0.9,
    scale = 8,
    n = 5,
    legend.lwd.is.portrait = F,
    title.lwd = "Estimation of daily commuting trips"
  ) +
  tm_legend(
    legend.position = c("left", "bottom"),
    legend.width = 0.55,
    legend.format = list(
      fun = function(x)
        formatC(x, digits = 0, format = "f")
    )
  ) + tm_shape(dus_centroid %>% top_n(50, internal)) + tm_bubbles(col = "#B02430",
                                                                  size = 0.6,
                                                                  border.lwd = 0) + tm_text(text = "community", col = "white", size = 0.6)

fig3a <- dus_fill + towns_plot + dus_outline + tm_layout(frame = F)
fig3b <- dus_fill_no_legend + towns_plot + dus_outline + dus_line_plot + tm_layout(frame = F)

tmap_arrange(list(fig3b, fig3a), ncol = 2)

#tmap_save(tmap_arrange(list(fig3b, fig3a), ncol = 2), filename = "Figure3.pdf", width = 7.5, height = 4.5)
```

## Figure 4
```{r fig.height = 4.5, fig.width = 7.5}
# the edges between communities in the CP system are based on shopping flows
cp_flow <- read_csv(here("analysis", "data", "raw_data", "centralplace_pc_edges.csv"))
cp_flow <- tesgcontainmentconnectivity::merge_flow(cp_flow, cp_com[[cp_i]], isolates)

cp_final <- tesgcontainmentconnectivity::com_statsPerCom(cp_com[[cp_i]], centralplace, isolates) %>%
  filter(internal > 1000) %>% 
  mutate(balance = incoming - outgoing) %>% 
  mutate(incomeRel = incoming / internal)
cp_final_sf <- tesgcontainmentconnectivity::comm_merge(cp_com[[cp_i]], postcode_with_isolates_merged, cp_i) %>% 
  left_join(cp_final, by = c("community" = "com")) %>% 
  ms_simplify(keep = 0.9, keep_shapes = T) # clean up some weird lines after merging


cp_centroid <- st_centroid(tesgcontainmentconnectivity::comm_merge(cp_com[[cp_i]], postcode_with_isolates_merged, cp_i)) %>% select(community) %>% left_join(., cp_final, by = c("community" = "com"))

cp_lines <- cp_flow %>%
  left_join(cp_centroid, by = c("source" = "community")) %>%
  left_join(cp_centroid, by = c("sink" = "community")) %>%
  rowwise() %>%
  mutate(geometry = st_combine(c(geometry.x, geometry.y)) %>% st_cast("LINESTRING")) %>% select(-geometry.x, -geometry.y) %>%
  st_as_sf(crs = 28992)

cp_fill <-
  tm_shape(cp_final_sf) + tm_fill(
    col = "incoming",
    palette = "GnBu",
    showNA = F,
    n = 5,
    style = "jenks",
    legend.is.portrait = F,
    title = "Incoming Interactions"
  ) +
  tm_legend(legend.position = c("left", "bottom"),
            legend.width = 0.55)
cp_outline <-
  tm_shape(cp_final_sf) + tm_borders(lwd = 0.9, col = "#383838")

cp_fill_no_legend <-
  tm_shape(cp_final_sf) + tm_fill(
    col = "incoming",
    palette = "GnBu",
    showNA = F,
    n = 5,
    style = "jenks",
    legend.is.portrait = F,
    title = "Incoming Interactions",
    legend.show = F
  ) +
  tm_legend(legend.position = c("left", "bottom"),
            legend.width = 0.55)
cp_line_plot <-
  tm_shape(cp_lines) + tm_lines(
    col = "#B02430",
    lwd = "weight",
    alpha = 0.9,
    scale = 7,
    n = 5,
    legend.lwd.is.portrait = F,
    title.lwd = "Estimation of daily shopping trips"
  ) +
  tm_legend(
    legend.position = c("left", "bottom"),
    legend.width = 0.55,
    legend.format = list(
      fun = function(x)
        formatC(x, digits = 0, format = "f")
    )
  ) + tm_shape(cp_centroid %>% top_n(50, internal)) + tm_bubbles(col = "#B02430",
                                                                 size = 0.6,
                                                                 border.lwd = 0) + tm_text(text = "community", col = "white", size = 0.6)

fig4a <- cp_fill + towns_plot + cp_outline + tm_layout(frame = F)
fig4b <- cp_fill_no_legend + towns_plot + cp_outline + cp_line_plot + tm_layout(frame = F)

tmap_arrange(list(fig4b, fig4a), ncol = 2)
# tmap_save(tmap_arrange(list(fig4b, fig4a), ncol = 2), filename = "Figure4.pdf", width = 7.5, height = 4.5)
```

## Figure 5
```{r fig.height = 4.5, fig.width = 7.5}
# the edges between communities in the export base system are based on business trips
# because these are relatively infrequent between postcodes, the filtered (>5 trips) aggregated postcode OD matrix would suppress too many connections
# instead we share the aggregated community matrix, which has been constructed using the `tesgcontainmentconnectivity::merge_flow` function used for both the DUS and CP data above
ex_flow <- read_csv(here("analysis", "data", "raw_data", "export_community_edges.csv"), col_types = list("c", "c", "d","d"))

ex_final <- tesgcontainmentconnectivity::com_statsPerCom(ex_com[[ex_i]], export, isolates) %>% 
  filter(internal > 1000)
ex_final_sf <- tesgcontainmentconnectivity::comm_merge(ex_com[[ex_i]], postcode_with_isolates_merged, ex_i) %>% 
  left_join(ex_final, by = c("community" = "com")) %>% 
  ms_simplify(keep = 0.9, keep_shapes = T) # clean up some weird lines after merging



ex_centroid <- st_centroid(tesgcontainmentconnectivity::comm_merge(ex_com[[ex_i]], postcode_with_isolates_merged, ex_i)) %>% select(community)

ex_lines <- ex_flow %>%
  left_join(ex_centroid, by = c("source" = "community")) %>%
  left_join(ex_centroid, by = c("sink" = "community")) %>%
  rowwise() %>%
  mutate(geometry = st_combine(c(geometry.x, geometry.y)) %>% st_cast("LINESTRING")) %>% select(-geometry.x, -geometry.y) %>%
  st_as_sf(crs = 28992)

ex_fill <-
  tm_shape(ex_final_sf) + tm_fill(
    col = "outgoingRel",
    style = "jenks",
    palette = "RdPu",
    showNA = F,
    legend.is.portrait = F,
    title = "% Outgoing Interaction"
  ) +
  tm_legend(
    legend.position = c("left", "bottom"),
    legend.width = 0.55,
    legend.format = list(
      text.separator = "to",
      fun = function(x)
        paste0(formatC(
          x * 100, digits = 1, format = "f"
        ), "%")
    )
  )

ex_outline <-
  tm_shape(ex_final_sf) + tm_borders(lwd = 0.9, col = "#383838")

ex_fill_no_legend <-
  tm_shape(ex_final_sf) + tm_fill(
    col = "outgoingRel",
    style = "jenks",
    palette = "RdPu",
    showNA = F,
    legend.is.portrait = F,
    title = "% Outgoing Interaction",
    legend.show = F
  )
ex_line_plot <-
  tm_shape(ex_lines) + tm_lines(
    col = "#B02430",
    lwd = "weight",
    alpha = 0.9,
    scale = 7,
    n = 5,
    legend.lwd.is.portrait = F,
    title.lwd = "Estimation of daily business trips"
  ) +
  tm_legend(
    legend.position = c("left", "bottom"),
    legend.width = 0.55,
    legend.format = list(
      fun = function(x)
        formatC(x, digits = 0, format = "f")
    )
  ) + tm_shape(ex_centroid) + tm_bubbles(col = "#B02430",
                                         size = 0.6,
                                         border.lwd = 0) + tm_text(text = "community", col = "white", size = 0.6)

fig5a <- ex_fill + towns_plot + ex_outline + tm_layout(frame = F)
fig5b <- ex_fill_no_legend + towns_plot + ex_outline + ex_line_plot + tm_layout(frame = F)

tmap_arrange(list(fig5b, fig5a), ncol = 2)
# tmap_save(tmap_arrange(list(fig5b, fig5a), ncol = 2), filename = "Figure5.pdf", width = 7.5, height = 4.5)
```

## Figure 7
```{r fig.height = 4.5, fig.width = 7.5}
postcode_all_systems <- postcode_with_isolates_merged %>% 
  left_join(ex_com[[ex_i]], by=c("pc4" = "name")) %>% 
  rename("exp" = "community") %>% 
  left_join(cp_com[[cp_i]], by=c("pc4" = "name")) %>% 
  rename("cp" = "community") %>% 
  left_join(dus_com[[dus_i]], by=c("pc4" = "name")) %>% 
  rename("dus" = "community") %>% 
  as_tibble() %>%
  filter(!(is.na(exp) | is.na(cp) | is.na(dus)))

match_ex <- postcode_all_systems %>%
  group_by(pc4) %>%
  nest() %>%
  mutate(ex = purrr::map(data, function(x) x$exp == postcode_all_systems$exp)) %>%
  select(pc4, ex)

match_cp <- postcode_all_systems %>%
  group_by(pc4) %>%
  nest() %>%
  mutate(cp = purrr::map(data, function(x) x$cp == postcode_all_systems$cp)) %>%
  select(pc4, cp)

match_dus <- postcode_all_systems %>%
  group_by(pc4) %>%
  nest() %>%
  mutate(dus = purrr::map(data, function(x) x$dus == postcode_all_systems$dus)) %>%
  select(pc4, dus)

match_all <- left_join(match_ex, match_cp) %>%
  left_join(match_dus)

t_ex <- match_all %>% 
  rowwise() %>% 
  mutate(n11 = sum(unlist(cp) & unlist(ex))) %>% 
  mutate(n00 = sum(!unlist(cp) & !unlist(ex))) %>% 
  mutate(n10 = sum(unlist(cp) & !unlist(ex))) %>% 
  mutate(n01 = sum(!unlist(cp) & unlist(ex))) %>% 
  mutate(wallace1_ex = n11 / (n11 + n10)) %>% 
  mutate(wallace2_ex = n11 / (n11 + n01)) %>% 
  mutate(jaccard_ex = n11 / (n11 + n01 + n10)) %>% 
  select(-ex, -cp, -dus)

t_ex %>%
  ungroup() %>% 
  summarise(n11 = sum(n11), n10 = sum(n10), n01 = sum(n01)) %>% 
  mutate(wallace1_ex = n11 / (n11 + n10)) %>% 
  mutate(wallace2_ex = n11 / (n11 + n01)) %>% 
  mutate(jaccard_ex = n11 / (n11 + n01 + n10))

t_cp <- match_all %>% 
  rowwise() %>% 
  mutate(n11 = sum(unlist(dus) & unlist(cp))) %>% 
  mutate(n00 = sum(!unlist(dus) & !unlist(cp))) %>% 
  mutate(n10 = sum(unlist(dus) & !unlist(cp))) %>% 
  mutate(n01 = sum(!unlist(dus) & unlist(cp))) %>% 
  mutate(wallace1_cp = n11 / (n11 + n10)) %>% 
  mutate(wallace2_cp = n11 / (n11 + n01)) %>% 
  mutate(jaccard_cp = n11 / (n11 + n01 + n10)) %>% 
  select(-ex, -cp, -dus)

t_cp %>%
  ungroup() %>% 
  summarise(n11 = sum(n11), n10 = sum(n10), n01 = sum(n01)) %>% 
  mutate(wallace1_ex = n11 / (n11 + n10)) %>% 
  mutate(wallace2_ex = n11 / (n11 + n01)) %>% 
  mutate(jaccard_ex = n11 / (n11 + n01 + n10))

pc_wallace <- left_join(t_ex, t_cp, by = c("pc4" = "pc4")) %>%
  select(-starts_with('n')) %>% 
  mutate(mean_wall = mean(c(wallace1_ex, wallace1_cp))) %>% 
  left_join(postcode_with_isolates_merged) %>%
  st_as_sf()


ex_outline_thick <- tm_shape(ex_final_sf) + tm_borders(lwd = 1, col = "black")

wallace_fill <-
  tm_shape(pc_wallace) + tm_fill(
    col = "mean_wall" ,
    palette = "-BuPu",
    style = "jenks",
    legend.is.portrait = F,
    title = "Mean Wallace I Index"
  ) +
  tm_legend(legend.position = c("left", "bottom"),
            legend.width = 0.55)

fig7a <- wallace_fill + towns_plot + ex_outline_thick + tm_layout(frame = F)

wallace_binary <-
  tm_shape(pc_wallace) + tm_fill(
    col = "mean_wall",
    palette = c("#810f7c", "#edf8fb"),
    breaks = c(0, 0.95, 1),
    legend.is.portrait = F,
    title = "Mean Wallace I Index"
  ) +
  tm_legend(legend.position = c("left", "bottom"),
            legend.width = 0.55)

fig7b <- wallace_binary + towns_plot + ex_outline_thick + tm_layout(frame = F)

tmap_arrange(list(fig7a, fig7b), ncol = 2)
# tmap_save(tmap_arrange(list(fig7a, fig7b), ncol = 2), filename = "Figure7.pdf", width = 7.5, height = 4.5)
```
